Starspots on sub sub giants

### 2020-10-16 document/ms.tex
Tick off a task on the writing todo list
Slight intro text changes

We measure the starspots on a sub sub giant.

@@

\section{Introduction}\label{sec:intro}

Sub-subgiant stars are stars that lie below the subgiant branch on a cluster optical color-magnitude diagram (CMD), but are too red to be main sequence stars. These stars are commonly found in evolved open clusters and globular clusters, with 65 sub-subgiants currently identified across 17 different clusters \citep{geller17}. The majority of sub-subgiant stars are single-lined spectroscopic binaries with short orbital periods of a few days with moderate X-ray luminosities of $10^{30}$ to $10^{31}$ erg s$^{-1}$ \citep[and references therein]{geller17}.

@@

\section{Analysis}
\begin{itemize}
\item Summary and assumptions of our methods
\item K2 data
\begin{itemize}
  \item Zero points with FFIs or super stamps
  \item Interpreting lightcurves
  \item Period and amplitude of lightcurve, with multi-term Lomb-Scargle + Fourier reconstruction
\end{itemize}
\item Phase folded archival V-band photometry (ASASSN+)
\subsection{IGRINS two-temperature spectral inference w/ Starfish}

>>>>

We measure the starspots on a sub-subgiant.

@@

\section{Introduction}\label{sec:intro}
Recent studies illuminate the important role stellar magnetic activity plays in stellar structure. This impact of stellar activity and magnetic fields is seen throughout the Herzsprung-Russell Diagram. For example, by biasing isochronal ages of young clusters \citep{somers15}, inflating radii of active M-dwarfs (Torres2010, Morales2010, Jackson2019), causing redder multiple turnoffs in stellar clusters [Bastian2009, Sun2019], and altering the pulsation modes of red giants [Gaulme2020]. As our ability to probe the detailed physics of stellar evolution continues to improve we must grapple with the complexities of stellar structure diverging from simpler theoretical expectations due to magnetic activity, which requires careful observational studies of magnetically active systems to test magnetic stellar models.

One example of the impact of magnetic activity is seen in sub-subgiant (SSG) stars, defined to be stars that lie below the subgiant branch on a cluster optical color-magnitude diagram (CMD), but are too red to be main sequence stars. Sub-subgiant stars are stars that lie below the subgiant branch on a cluster optical color-magnitude diagram (CMD), but are too red to be main sequence stars. These stars are commonly found in evolved open clusters and globular clusters, with 65 sub-subgiants currently identified across 17 different clusters \citep{geller17}. The majority of sub-subgiant stars are single-lined spectroscopic binaries with short orbital periods of a few days with moderate X-ray luminosities of $10^{30}$ to $10^{31}$ erg s$^{-1}$ \citep[and references therein]{geller17}.

@@

\section{Analysis}
\begin{itemize}
\item Summary and assumptions of our methods
\item K2 data
\begin{itemize}
  \item Zero points with FFIs or super stamps
  \item Interpreting lightcurves
  \item Period and amplitude of lightcurve, with multi-term Lomb-Scargle + Fourier reconstruction
\end{itemize}
\item Phase folded archival V-band photometry (ASASSN+)

\subsection{IGRINS two-temperature spectral inference w/ Starfish}
